Multifluid model of a one-dimensional steady state force-free current sheet

### 2024-06-07 index.qmd
new: add velocity profiles for identical asympotic magnetic field

@@

@@

>>>>

#### MHD in a nutshell

$$
\begin{aligned}
& \frac{\partial \rho}{\partial t}+(\vec{V} \cdot \nabla) \rho+\rho \nabla \cdot \vec{V}=0 \\
& \rho\left[\frac{\partial \vec{V}}{\partial t}+(\vec{V} \cdot \nabla) \vec{V}\right]+\nabla p=\vec{J} \times \vec{B} \\
& p=\alpha \rho^\gamma \\
& \nabla \times \vec{B}=\mu_0 \vec{J} \\
& \frac{\partial \vec{B}}{\partial t}=\nabla \times(\vec{V} \times \vec{B})
\end{aligned}
$$

@@

For the same asymptotic magnetic field, it is interesting to see how the plasma profiles change with different system parameters.

$$
\text{cond}(n(z), λ_{n,∞}, λ_{z,∞}) = 0
$$

Here we set $B_y(z=\infty) = 1/2 B_y(z=0)$ and $B_0 = 2 B_z$, and fix $λ_{z,∞} = -1$. By varying $λ_{n,∞}$, we find that the magnetic field profiles are exactly the same, while plasma velocity profiles vary. We normalize the plasma velocity by asympotic Alfvén velocity $v_{A,∞} = B_0 / \sqrt{n}$, and the profiles are plotted below @fig-uxnorm. It could be seen that for $λ_{n,∞} = 1$, we have zero bulk velocity change across the current sheet in the asymptotic limit.

::: {.column-screen-inset}
::: {#fig-profiles layout-nrow="1" }

![Magnetic field, ion density, and out ion bulk velocity for $λ_{n,∞}=1$ and $λ_{z,∞}=-1$.](figures/profiles_ratio=0.5.svg){#fig-profiles_ratio}

![Normalized Plasma Velocity $U_x$ Profiles for Different $λ_{n,∞}$.](figures/UxNorm.svg){#fig-uxnorm}

![Normalized Plasma Velocity $U_y$ Profiles for Different $λ_{n,∞}$.](figures/UyNorm.svg){#fig-uynorm}

:::
:::

![](figures/vRatios.svg)

@@

```mathematica
conf = {ratio -> 1/2}
TextString[conf]
<!-- Convert a dict-like configuration to a string -->
saveName[c_] := StringJoin[ToString /@ c]
```
